Strong lensing selection effects

### 2022-08-02 paper/seleff.tex
added psf

>>>>

All of the examples that we considered were based on sources with a single surface brightness peaks.
In general this is not necessarily the case, and the intrinsic number of surface brightness peaks of a strongly lensed source is not known a priori.
When dealing with a real lens candidate, applying our lens definition criterion requires showing that the observed number of surface brightness peaks can be reproduced with a lens model in which the source has a smaller number of peaks.
In samples of lenses defined via visual inspection this process is typically done implicitly, by identifying multiply imaged blobs that belong to the same source element.
%Applying our lens definition criterion to a real lens requires showing that the observed number of surface brightness peaks can be reproduced with a lens model in which the source has a smaller number of peaks.
